\pagestyle{empty}

{\large\itshape

Black Leaf’s Spirit Form flew down and surveyed the scene.

Her followers had quite an army down there, and they looked like they would need all the help they could get if they were to win the battle. Those gnolls were tough, and unusually organized.

She knew why, of course. Grakklak Bonegnawer had been doing his best to inspire his race to greatness, and had worked hard to get his creations to unite their tribes. She respected that, and had told him so. But she wasn’t going to let the gnoll empire march over her people’s lands. Unfortunately her attempts at diplomacy with the Immortal patron of gnolls had failed, so here she was.

Black Leaf thought briefly about manifesting her Embodied Form and routing the gnolls herself. After all, even an army of gnolls would be no match for her Immortal power. The thought quickly passed. There would be many eyes watching this battle, and being caught directly interfering on the prime plane would cause her no end of trouble...

No, there were only two choices. She could appear as Azelda the Mighty, a mortal dragon body that she donned occasionally to dispense oracular advice from, and hope that Azelda could help turn the tide of battle; or she could appear in a vision to her priests and warn them to retreat and fight another day. Flying over the enemy lines, she realized that Grakklak had over extended himself; a serious mistake to make. His famed troll-smasher brigade wasn’t here and neither was Urlak, his preferred Mortal Form. They must be aiding the other front in his battle. Trust a barbarian to attack on two fronts at the same time, overconfident as always.

Although he had no reason to know that Azelda was really one of Black Leaf’s Mortal Forms, he really should have known that the dragon would help the Halderites in their time of need and prepared for her to be in this fight. Not doing so was a bad mistake.

With a smile, Black Leaf flew into a nearby cave and shifted form to her mortal dragon body. She would lead the army from the front, and help them win the battle at the cost of Azelda’s life. It was worth losing the form to set such an example for them. She could easily make another, and she was confident that Grakklak wouldn’t try anything while she was recovering.

Black Leaf looked over the precipice at the whirling vortex of energy below and smiled.

“No problem.”, she said, “There’s a bit of an overhang but I can climb down, no problem.”

Her face suddenly turned pale.

“But THAT is a problem!”, she shouted—pointing behind the rest of the party.

The other spun around and were shocked to see a swarm of flying creatures rounding the corner, each one a ball of tentacles the size of a man.

“Looks like someone doesn’t want this artifact destroyed...” muttered Aloysius and started preparing some kind of spell.

Countess Black listened to the village elder’s plea. He was very grateful for the extra guards that she’d assigned to the area, and the petty banditry had now been brought under control. However, the remaining bandits had allied with a local orc tribe: using the orcs as muscle to raid towns and then selling the trade goods—and slaves—that the orcs acquired. The guards were simply not able to cope.

The countess sighed. With Lord Thalx testing her borders at every turn she had hardly the army to spare as it was; and she certainly didn’t want to hire the Gray Eagle mercenaries again after the trouble that Count Oeric had had with them.

She held up her hand for the elder to be quiet, and beckoned over her herald.

“Jabe, go see the new sheriff and find out what the going rate is for adventurers these days. We only need a bunch that can take out orcs and bandits, so we’re looking for reasonable experience—we don’t need to pay for dragon slayers or anything silly like that. If it’s over 2,000 gold then come back and check with me first, otherwise go ahead and make it known that we’re hiring. You know what you’re doing, so I’ll leave it up to you to work out how to find adventurers without alerting the bandits that we know what they’re up to. If the bandits have been selling slaves, we may need to follow this up by checking out who they’re selling them to—so get the adventurers to report to me before they set off.”

Baroness Black looked at herself in the mirror and admired her reflection. The dress had cost her a small fortune, but she could afford it now. And it was worth it. The queen herself had commented on it during the investiture ceremony.

Just yesterday she’d been plain old Black Leaf. But now she was a baroness. And all for slaying a dragon.

\newpage

Well, that wasn’t strictly true. The dragon was just the latest thing they’d done for the King Elberet. There was also the matter of the trolls; and that assassin cult that they’d destroyed; and the vampire with the undead army...

She shuddered at the memory of the undead army. Undead really weren’t her thing and she’d actually died fighting those awful spectres. Luckily, Elfstar had been able to revive her before she turned into one herself; but she still had nightmares where she could feel their icy touch and feel her life being sucked from her.

Black Leaf shook herself out of her reverie, and got changed out of her finery into more comfortable garb; chuckling to herself at the absurdity of finding armor and weapons more comfortable than fancy dresses. Still, there was work to be done. The king was no fool, and the posh new titles that they’d all received had come with adjacent land grants. Land that was, not coincidentally, wild, dangerous and untamed. They were going to need to work together if they were going to clear the land and attract settlers; and they were supposed to be meeting with the royal cartographer tonight—and Black Leaf was damned if she wasn’t going to sneak a look at the maps beforehand to make sure there were no big surprises in store.

Black Leaf waved frantically at her companions to get them to stop their whispered conversation, and ever so gently pressed her ear to the door. She could just make out the faint sounds of chanting in a long dead language.

She turned back to the rest of the group, and motioned them back to a safe distance; wincing as Oeric stomped back seemingly oblivious to all the noise his new armor was making.

“Okay, this is it guys!” she whispered after creeping away from the door;

“From the sounds of it, that priest is through there; and he’s just starting the ritual. If we burst in and attack, we should be able to rescue the kids before...”

Black Leaf didn’t finish her sentence. She didn’t need to. They all knew what would happen if they didn’t stop the priest.

There was a brief moment of silence as they were all lost in thought, before Gretchen broke the tension in her usual quiet and reassuring way:

“Okay, I know none of us have done this sort of thing before, and I know we’re all scared; but we all fought very well against those goblins on the way in here. You make me proud to be a member of this team, and I know we can do this. Elfstar—you be on the look out for those skeletons that we heard about. We haven’t seen them yet, so they may be guarding the place and you have a good chance of being able to keep them away from us. Oeric—you and I will charge in and start fighting. Black Leaf—follow us in and try to sneak around and release the kids while the priest is occupied with us; then see if you can stab him in the back. Al—You haven’t used your magic yet, so you hang back and I’ll trust you to use it whenever it seems best.

Everyone ready? Then let’s go.

3... 2... 1... NOW!”

Black Leaf tried to control her breathing as she ran into the room after the others. Adrenaline had kicked in and she was fighting to keep calm and controlled.

She saw the priest look up in surprise as the large warrior and the dwarven woman charged straight at him. He had an orcish bodyguard, and—damn it—there was another orc guarding the prisoners.

Taking advantage of the distraction of the charge, Black Leaf ducked into the shadows at the side of the room and crept towards the orc guarding the prisoners. He was foolishly dithering between keeping at his post and going to join in the main fight. Slipping behind him unseen, Black Leaf stabbed him in the gut with her dagger; forcing it up between the leather bands of his armor. As she did so she saw an arrow made of some kind of magical glowing force streak across the room, curve round the priest’s bodyguard, and slam into the side of his helmet; making him stumble and causing the magical energies he was summoning to disperse.

Maybe they would succeed, after all...
\normalfont}

